
\section*{The effects of COVID19 on this thesis.}
\begin{itemize}

\item One person in my house caught had symptoms of COVID19, and so I had to self-isolate
      for the first period of 14 days.

\item I had to take care of my partner whilst
      they had a fever, and subsequently self-isolate for an additional 14 days.

\item We both lived and worked in around 9 m$^{2}$ of floor space, which is not as
      good a work environment as an office.

\item I was less able to collaborate with other members
      of the British Antarctic Survey due to not being in the office.

\item Some of my notes, and my official lab-book were locked into my BAS office when full lockdown was declared,
      as I only had access to a small amount of car space to bring my material back.
      I therefore had to find similar material elsewhere. This wasn't a serious inconvenience,
      but it did waste some time. Perhaps this was my fault for not seeing where government policy was going.

\item I had the misapprehension that the lockdown would have ended in time for me to
      reclaim my official lab-book before hand in.

\item Having said all this, I was mainly able to carry on as normal because
      my work is computer-based, and so I was much less impacted than an experimentalist.
      Without this project to do, lockdown would have been much less tolerable,
      and I am proud of the work that I managed to finish.

\item I was also lucky to be able to able to present to in the CEDSG-AI4ER series
      the week before the first lockdown measures were put in place, and
      I found the feedback the audience gave very helpful.

\item My supervisor Dr.~Dan~Jones was also supportive,
      and we continued to have supervisory meetings over zoom,
      sometimes with Dr.~Laure~Zanna (NYU), and these provided some much
      needed structure.

\end{itemize}

[Non COVID related problems are discussed in the `deadends' section of the
appendix to this thesis.]

\newpage
[column left intentionally blank]

\newpage

[page left intentionally blank]
\newpage
