\subsubsection{NEMO models}
\paragraph{Introduction}
\label{sec:nemo}
I was able to use two outputs~ยง~\ref{sec:rean-prod}~\&~ยง~\ref{sec:control-1950-intro}
of use the European NEMO ocean engine~\cite{madec2015nemo}, which uses the ORCA12 grid, with a  $\frac{1}{12}^{\circ}$
resolution.
This is a tripolar ocean grid, designed so that no coordinate singularities are in the ocean~\cite{madec1996global}.
Instead there are two `north' poles, one in Russia, and one in the Canada,
with the grid elegantly curving between the two.
The south pole remains in Antarctica, and the grid is undistorted from a lon-lat
 grid in the southern hemisphere.

 The Bathymetry used by the ocean engine is based on
 ETOPO2~\cite{lecointre2011definition,noaa20062}.\footnote{\url{https://www.ngdc.noaa.gov/mgg/global/etopo2.html}}
 This bathymetry is more accurate along the US coastline because it incorporates
 more direct measurements rather than relying on altimetry data. Table~\ref{tab:mod-symb}
 introduces the variables taken from NEMO.

\input{tables/model-symbols.tex}

\paragraph{Limitations}

Neither of the outputs in~ยง~\ref{sec:rean-prod}~\&~ยง~\ref{sec:control-1950-intro}
include tides, inundation (the flooding of land), or wave setup.
The resolution of the models mean that in the region of interest cells are around
8km wide. Therefore the centre at which the sea surface height is recorded,
is around 4km from the coast.

\subsubsection{2004-5 \texttt{two-year} hourly reanalysis product}
\label{sec:rean-prod}
Dr.~Pierre Mathiot kindly ran a global two year ocean simulation with
hourly outputs for the years 2004-5 (thus including a representation of Katrina as
in Figure~\ref{fig:katrina}).
It used EN4 for its initial conditions,
and CORE2 for its atmospheric forcing.

\paragraph{EN4 initial conditions}
EN4 is a product that uses all available ocean profiles
(through the ARGO program etc.)~\cite{good2013en4, HadObs}
to produce a best guess as to what the salinity and temperature of the ocean is.
 The start of this reanalysis product is 1976.


\paragraph{CORE2 forcing}
CORE2 is a set of global air-sea fluxes~\cite{griffies2012datasets,large2009global,
 hurrell2008new, core2, core2expert}.\footnote{\url{https://climatedataguide.ucar.edu/climate-data/corev2-air-sea-surface-fluxes}}
 The primary data source is the NCEP/NCAR R1 reanalysis product, but bias corrected
 with more reliable remote and local sensing data.

\input{figures/katrina.tex}
