\section{Acknowledgements}
Dr.\ Dan Jones (British Antarctic Survey)
has been an invaluable help throughout this project.
Dr.\ Laure Zanna (New York University)
 was a useful counsel as to what is feasible,
 and what the common views in the literature were.
Dr.\ Pierre Mathiot (Met Office) also deserves my thanks for
producing the high-resolution ORCA12 data that I used, and
for answering my queries.
I also received advice from Dr.\ Rory Bingham (Bristol).
I hope that in the fullness of time these collaborators will become
co-authors, as we expand and publish the work begun here.

I also received useful feedback from the CEDSG-AI4ER group,
after my presentation on 10th March 2020.
PRIMAVERA received funding from the European Union's Horizon 2020
Research and Innovation Programme under grant agreement no.~641727.


\section{Resources used}

This report was typeset in \LaTeX\
with \texttt{matplotlib}~\cite{Hunter:2007} and \texttt{draw.io}~\cite{DrawIO}
for original figures, WebPlotDigitiser for data extraction~\cite{WebPlotDigitiser},
and Mathpix for maths extraction~\cite{mathpix}.
It makes extensive uses of the \texttt{sklearn} library~\cite{scikit-learn} as highlighted in the report.
The \texttt{cmocean} package~\cite{thyng2016true}\footnote{\url{https://matplotlib.org/cmocean/}}
provided oceanography standard colour maps, \texttt{numba.jit}~\cite{lam2015numba} for speed,
\texttt{xarray}~\cite{hoyer2017xarray} for ND~data.
I used Panolpy and \texttt{ncview}\footnote{\url{http://meteora.ucsd.edu/~pierce/ncview_home_page.html}}
for inspecting NetCDF files.

I made use of these textbooks:~\cite{roisin2010GFD,williams2011ocean,ITILA,
sivia2006data,williams2006gaussian,
}.\footnote{\url{http://www.gaussianprocess.org/gpml/chapters/RW.pdf
}}
I found Stephen Pinker's book~\cite{pinker2015sense} especially useful and entertaining.
Any errors in writing are my own, but this book does defend the selective use of the
passive voice, if either its presence or absence in certain sections frustrates the reader.
I felt more comfortable with directly talking about cause after reading
Judea Pearl's \textit{The Book of Why}~\cite{pearl2018book}.

The code listing for this report is available as a \texttt{python3} repository on Gitlab~\cite{gitlab, skextremes}.
 I have tried to write using PEP8 style\footnote{\url{https://www.python.org/dev/peps/pep-0008/}}
 and have been helped by \texttt{pylint} and Pycharm.\footnote{\url{https://www.jetbrains.com/pycharm/download/}}
 Errors are dealt with as per the Physics formula booklet~\cite{MathsFormulaBooklet}
 by the \texttt{python3.uncertainties}
 package~\cite{lebigot2010uncertainties}.\footnote{\url{https://pythonhosted.org/uncertainties/}}

 To move and process the large quantity of climate data on the HPCs I used \texttt{tmux}
 to run \texttt{bash}, \texttt{python3}, and \texttt{fortran} scripts.
