\section{Preprocessing coastal data}
The sea surface height in the model is relative to
a reference geoid: the surface that a homogeneous static fluid would occupy
on an azimuthally symmetric Earth of the same size and rotation frequency.
Dynamic topography emerges because of the
currents and density contrasts (Figures~\ref{fig:zos}~\&~\ref{fig:ssh_stats_america}A).
\input{figures/2d_fields/zos.tex}



We define the third  moment around the mean,

\begin{equation}
\operatorname{Skew}[X]\equiv \mathrm{E}\left[\left(\frac{X-\mu}{\sigma}\right)^{3}\right]
=\frac{\mathrm{E}\left[(X-\mu)^{3}\right]}{\left(\mathrm{E}\left[(X-\mu)^{2}\right]\right)^{3 / 2}},
\end{equation}

and fourth as the excess above the Gaussian~\cite{taleb2019statistical},

\begin{equation}
\operatorname{Kurt}[X]=
\mathrm{E}\left[\left(\frac{X-\mu}{\sigma}\right)^{4}\right]-3
\equiv \frac{\mathrm{E}\left[(X-\mu)^{4}\right]}{\left(\mathrm{E}\left[(X-\mu)^{2}\right]\right)^{2}}-3.
\end{equation}



\input{figures/stats_zos}


These are useful to summarise the SSH statistics
for \texttt{eUS} in Figure~\ref{fig:ssh_stats_america}.\footnote{
The individual points' SSH (Figure~\ref{fig:individual_zos} in ยง~\ref{sec:sum-var-stat}),
do not reveal any discontinuity in the data in \texttt{tyr},
 but Figures~\ref{fig:four-trans-panels}-\ref{fig:mm-hp-lp}
suggest that the displacement might be caused by \texttt{tyr} spin up from the
initial conditions.
}
On the right of panels \ref{fig:ssh_stats_america}A--D
is the Pearson regression coefficient, $r_p$,
between the two years for that moment, which shows that the mean and
std~dev of a point are c.~static between the years,
but the higher order moments of skew and kurtosis
(\ref{fig:ssh_stats_america}~C~\&~D) are more sensitive to the
random incidence of storms on the coast.


\label{sec:fourier}

The Fourier transform is defined as,

\begin{equation}
F(f)=\int_{-\infty}^{\infty} y(x) e^{-i 2\pi f x} d x,
\end{equation}

which in discrete form~\cite{cooley1965algorithm} is,


\begin{eqnarray}
\sum_{n=0}^{N-1} a_{n} e^{-2 \pi i  k n/ N}=&\sum_{n=0}^{N / 2-1} a_{2 n}
e^{-2 \pi i k (2 n)/ N}  \\ &+\sum_{n=0}^{N / 2-1} a_{2n+1} e^{-2 \pi i k (2 n+1)/ N}. \notag
\end{eqnarray}

Fourier transforms of real signals have Hermitian symmetry,

\begin{equation}
\mathcal{F}{(-g(x))}=\mathcal{F}(g(x))^{*},
\end{equation}

implies that negative frequencies have no information not in the positive.


Figures~\ref{fig:zm_fft_zos}~\&~\ref{fig:zm_fft_tos} give the
Fourier transform spectrums of SSH and SST respectively.
Figures~\ref{fig:zm_fft_zos} shows that SSH has a red-noise spectrum,
which is true of the ocean in general, and Figure~\ref{fig:zm_fft_tos}
shows that SST is dominantly annual (as expected).
The relationship between the temperature and the sea surface temperature.
The Florida current is a likely source of particularly red noise at Miami
(Figures~\ref{fig:vos}~\&~\ref{fig:uos}).
The general eddy activity is visible in Figures~\ref{fig:vos}~\&~\ref{fig:uos}
as the loop current has formed a secondary vortex ring moving northwards
in Figures~\ref{fig:uos}~to~\ref{fig:vos}.
Figures~\ref{fig:no-hp-lp}~\&~\ref{fig:mm-hp-lp} show a high and
low pass filter applied to specific points, and Figure~\ref{fig:four-trans-panels}.


\Delta\eta_{\;\mathrm{lp}}(t) = \int_{\mathbb{R}}W\left(\frac{|f|}
{|f|_{\mathrm{thresh}}}\right)\int_{\mathbb{R}}e^{2\pi i (t-t^{\prime})f }
\Delta \eta(t^{\prime})dt^{\prime}df
\end{equation}
\begin{equation}
\Delta\eta_{\;\mathrm{hp}}(t) = \int_{\mathbb{R}}\left(1-W\left(\frac{|f|}
{|f|_{\mathrm{thresh}}}\right)\right)\int_{\mathbb{R}}e^{2\pi i (t-t^{\prime})f}
   \Delta \eta(t^{\prime})dt^{\prime}df
\end{equation}

\input{figures/2d_fields/vos}
\input{figures/2d_fields/uos}


\input{figures/fourier-transform-panels.tex}

\input{figures/choose-thresh.tex}

\label{sec:lag}

\input{figures/lag-panels.tex}

We would like to be able to explain this seasonal cycle in SSH.
The obvious choice would be to look at SST and SSH, as in Figure~\ref{fig:ssh-sst}
for \texttt{eUS} for \texttt{tyr}, and do lag correlation, which is defined as:

\begin{equation}
r_{k}=
\frac{\sum_{i=1}^{N-k}\left(X_{i}
-\bar{Y}\right)\left(X_{i+k}-\bar{Y}\right)}
{\sum_{i=1}^{N}\left(X_{i}
-\bar{Y}\right)^{2}}.
\end{equation}

Figure~\ref{fig:lag-plot} (\texttt{eUS}, \texttt{tyr}) tells a simple story of
SSH lagging slightly behind SST, as the mixed layer takes longer
to heat up than the surface.
However Figure~\ref{fig:vc_lag-plot} undermines this as the
lag becomes anti-phase, falsifying this simple hypothesis as 
being generally true.

I suggest that Figure~\ref{fig:lpredthresh} justifies removing the low frequency
component of the signal, as it supports the hypothesis that the
low frequency signal is not caused by sea surface stress.

\FloatBarrier
