\section{Simple measures of responsiveness}
\label{sec:responsiveness}

\subsection{Thresholding $|U_{10}|^2$ responsiveness}
\label{sec:thresh-resp}

As shown in Figure~19~of~T20~\cite{ZannaPreprint} (see Figure~\ref{fig:yin-responsiveness}).
The threshold seems arbitrary,
so I chose that the $\Delta\eta_{\mathrm{hp}} \ge 0$ (Figure~\ref{fig:simple-responsiveness-results}),
as it approximately guarantees that the sea surface stress is acting into
the coast.


\subsection{$\tau_u$, $\tau_v$ responsiveness}
\label{sec:tau-tau}
This method is quite crude, and could be simply improved.
Figure~\ref{fig:tau-tau-r-no} shows a single example of working out the linear
responsiveness in \texttt{tyr}, which is applied along \texttt{eUS} in
Figure~\ref{fig:tau-tau-resp}.
Figure~\ref{fig:tau-tau-responsiveness}
creates a more robust metric for the responsiveness.

\input{figures/responsiveness-indiv.tex}

\input{figures/simp-resp.tex}


\input{figures/responsiveness-page.tex}

\label{sec:angle}

Figure~\ref{fig:tau-tau-angle} shows that the angle is highly correlated with
the bearing of the coast (see~ยง~\ref{sec:convexity}).
This bearing is compared to the normal coastline bearing).
As shown in Figure~\ref{fig:tau-tau-angle}, there is a systematic offset between the two lines,
with a slight change between them, which can be explained through
 Ekman transport~\cite{hope2013hindcast}.


\label{sec:reg-metrics}

The magnitude of this regression line varies in approximately the same
way for both\footnote{QUANTIFY!!} (Figures~\ref{fig:simple-responsiveness-results},~\ref{fig:tau-tau-resp}~\&~\ref{fig:tau-tau-responsiveness}),
showing that there is some underlying property of the
coastline that both illuminate.
Figure~\ref{fig:learnt-eus}, uses lasso and ridge regression to
estimate the relationship between the coastal metrics (ยง~\ref{sec:convexity}~\&~\ref{sec:bath-grad})
and either responsiveness metric.
It is possible that this is a spurious structure, where the fit
is made possible by giving so many information-less channels to fit against.
We use \texttt{vc} and \texttt{jap} as in Figure~\ref{fig:learnt-vc},
to check that this generalises.

\label{sec:generalisability}


\input{figures/generalisability}



\FloatBarrier
